---
title: "Hydra report"
author: "Mattias  de Hollander (m.dehollander@nioo.knaw.nl)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
    rmd: "report.Rmd"
output:
  html_document:
    highlight: tango
    number_sections: no
    theme: default
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
      smooth_scroll: yes
---


# `r snakemake@config$project`

## Info
Forward primer: `r snakemake@config$forward_primer`

Reverse primer: `r snakemake@config$reverse_primer`

Silva database: `r basename(snakemake@config$silva_arb)`

### Input files

```{r kable, message=FALSE, warning=FALSE}
library(knitr)
kable(snakemake@config$data)
```

## Summary
Reads have been merged with `r snakemake@params[["mergemethod"]]`

## Plot
```{r cars, message=FALSE, warning=FALSE}
library(plotly)
readstat = read.csv(snakemake@input$readstat)
p <- ggplot(readstat, aes(y=readstat$avg_len, x = seq(1, length(readstat$avg_len)))) + geom_point()

ggplotly(p)
```


## phyloseq
```{r phyloseq, message=FALSE, warning=FALSE}
library(phyloseq)
import_biom(snakemake@input$biom)
```


## Files
<!--<script src="http://code.jquery.com/jquery-latest.min.js" type="text/javascript"></script>-->
<script>
function download(text, name, type) {
  var file = new Blob([text], {type: type})
  var a = $('<a id="download-it">Download BIOM file</a>').appendTo('body')
  a[0].href = URL.createObjectURL(file)
  a[0].download = name
}
function dataURItoBlob(dataURI, callback) {
    // convert base64 to raw binary data held in a string
    // doesn't handle URLEncoded DataURIs - see SO answer #6850276 for code that does this
    var byteString = atob(dataURI.split(',')[1]);

    // separate out the mime component
    var mimeString = dataURI.split(',')[0].split(':')[1].split(';')[0]

    // write the bytes of the string to an ArrayBuffer
    var ab = new ArrayBuffer(byteString.length);
    var ia = new Uint8Array(ab);
    for (var i = 0; i < byteString.length; i++) {
        ia[i] = byteString.charCodeAt(i);
    }

    // write the ArrayBuffer to a blob, and you're done
    var bb = new Blob([ab]);
    return bb;
}
</script>

<script>
dataURL = "`r base64enc::dataURI(file = snakemake@input$biom, mime = 'text/csv', encoding = 'base64')`"

download(dataURItoBlob(dataURL), "`r basename(snakemake@input$biom)`", 'text/plain')
</script>

<a download="report.Rmd" href="`r base64enc::dataURI(file = params$rmd, mime = 'text/rmd', encoding = 'base64')`">R Markdown source file (to produce this document)</a>


